Response to reviewers

### 2025-07-04 src/docs_paper-jtb/revisions.Rmd
Alter response on s and k

We agree that it would be of interest to explore the effect of choosing a different number of PCA components ($s$) and number of quadrature points per dimension ($k$).
One could also consider a varying number of quadrature points.
For example "gradually lowering $k$ over the principal components" presumably would be the most efficient approach.

>>>>

In the current work we focused on results which were as accurate as possible while still running in a practical amount of time.
We agree that it is possible that faster results that are nearly as accurate could be obtained using or procedure.
